%Input preamble
\input{HelperFiles/Resources}

\begin{document}

\title{Factor Analysis}
\author{Jorge Luis Garc\'{i}a\thanks{Department of Economics, the University of Chicago (jorgelgarcia@uchicago.edu).} $^{,}$\thanks{I thank Sneha Elango, Tim Kautz, and Bradley Setzler for helpful comments.}}
\date{First Draft: May 29, 2014 \\ This Draft: \today}
\maketitle


\begin{abstract}
\noindent The objective of this document is to describe a step-by-step methodology to extract factors, or underlying latent variables, from a set of observed measures. Factor analysis is arbitrary by construction. Thus, I intend to provide the exact steps for factor analyzing a set of measures and elect a consistent way of being arbitrary. The theoretical fundamentals of this document come from \citet{gorsuch1983factor}. Although this author (or any other author) does not suggest any method over the other, I justify why the methods I elect are simple and transparent. Finally, I provide implementations in Python and Stata in separate files.
\end{abstract}

%Diagonal Factor Analysis
\section{Diagonal Factor Analysis} \label{section:dfa}
\input{Sections/factors/setting}
\input{Sections/factors/notation}
\input{Sections/factors/method}
\input{Sections/factors/number}
\input{Sections/factors/annotations}

%Rotating the Factors Analysis
\section{Why Rotation Makes sense and How to Go about it?} \label{section:rfa}
\input{Sections/factors/rotateintro}



%\clearpage
\bibliographystyle{chicago}
\bibliography{BibtexFiles/Resources}
\clearpage

\end{document}